Genome-wide changes in expression during inflorescence architecture development

### 2015-08-14 ms.Rmd
uh oh, broke mfuzz results
could be ok like this...

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933}
print(f_mfuzzClusters)
```

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933, cache = TRUE}
print(f_mfuzzClusters)
```
